An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-09-30 nips_2016.tex
Updated Figure with logistic regression curves

Figure~\ref{fig:logistic_fig} shows the prediction accuracy and log likelihood
on the test set as a function of the cumulative training data points processed.
We see that our minibatch MH test
is more efficient; it has similar or better performance while consuming fewer
data points.

\begin{figure}[t]
    \centering
    \begin{subfigure}{.4\textwidth}
     \centering
     \includegraphics[width=1\linewidth]{LogisticRegressionResult/acc_logistic}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
     \centering
    \includegraphics[width=1\linewidth]{LogisticRegressionResult/ll_logistic}
\end{subfigure}
\caption{
    Logistic regression performance (accuracy/log likelihood) and minibatch size
    analysis. {\color{blue} Daniel: let's use matplotlib's ``subplot''
    functionality, so that the images appear the same size. We can handle this
    later; it will be easy.}
    }
\label{fig:logistic_fig}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{minibatch_size_logistic.png}
	\caption{
    Counts of minibatch sizes that the three methods used in the logistic
    regression experiment from Section~\ref{ssec:logistic}. It is analogous to
    Figure~\ref{fig:gauss_mix_2}.
    }
	\label{fig:logistic_minibatch}
\end{figure}

>>>>

Figure~\ref{fig:logistic_performance} shows the prediction accuracy and log
likelihood on the test set as a function of the cumulative training data points
processed.  We see that our minibatch MH test is more efficient; it has similar
or better performance while consuming fewer data points.

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{logistic_performance.png}
	\caption{
    Logistic regression performance (accuracy/log likelihood) based on
    cumulative data usage.
    }
	\label{fig:logistic_performance}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{minibatch_size_logistic.png}
	\caption{
    Counts of minibatch sizes that the three methods used in the MNIST logistic
    regression experiment from Section~\ref{ssec:logistic}. It is analogous to
    Figure~\ref{fig:gauss_mix_2}.
    }
	\label{fig:logistic_minibatch}
\end{figure}
